---
title: "Problem Set 1 - Preparations for 312"
output:
  html_document: 
    df_print: tibble
    highlight: pygments
---
-----


### NAME: Jingyi Fang
### USC ID: 8020938911
### People I discussed this with: Johnny Geng, Jing Zhao
### **DUE DATE: 1/16 at 11am **  

-----

# Setting Your Working Directory 

The first thing you want to do when using R or Rstudio is to set your "working directory".  R will assume that all of the files it needs to access are in this directory.  For this problem set, we will set the working directory to your "PS1" folder for problem set 1.

1. Any time you work in R, you can see the current working directory, by using the code, `getwd()`.  Try running this in the console (by typing getwd() followed by pressing Enter or Return).
```{r}

```

We would like to add that command to this document so that we can show someone else that we ran it.  We will do so by adding a code "Chunk" to our R Markdown document.  To do this, first click on the place in this document where you want the code chunk to be added, then click on the "Insert" button on the menu for this document and choose "R" (You can also press `cmd + option + i` on Mac or `ctrl + alt + i`).  R Markdown will insert the following:

```{r}

```
Notice, when you knit your html file, you will not see this code chunk since there is no code for R to run in it.  You will see several other code chunks throughout the document that contain R code, but the code has not been evaluated (these are highlighted in light gray). In this .Rmd document, the first line of these code chunks are all set to `eval=FALSE`. For these code chunks to be evaluated in your html document, you need to set `eval=TRUE`. For now, keep these code chunks set to `eval=FALSE`.

Now, we will use the `getwd()` function in R to determine your current working directory.  We will put this command in the code chunk below.  

Evaluate the following code in your html document, by changing the first line below to `eval=TRUE`. 

```{r,eval=TRUE}
getwd()
```

Knit your html document, and you will find the R code you used as well as the output from that code which is your current working directory for this R Markdown document. The working directory for an .Rmd document is always the same directory that contains the .Rmd document.

You might have noticed that the result of `getwd()` is different from what it was when you ran `getwd()` in the R Console.   You can easily change your working directory for the R Console through RStudio by choosing *Session -> Set Working Directory  -> Choose Directory*. For now, set your working directory to your folder called PS1. Check that this is your current working directory for the R Console by typing `getwd()` into the R Console below.


# Some Basic R Commands

1. At the most basic level, R can be used as a calculator. The following chunk of code gives some basic R commands for calculation.

```{r, eval=TRUE}
5 - 3
5 + 3
5 * 3
5 / 3
5 ^ 3
```

Now in the first line of this code chunk, set `eval=TRUE`. Knit your html to see these mathematical expressions evaluated in your html document file. 

For any code in your R Markdown document, you can also run it directly in your R console by highlighting the code you wish to run and choosing the "Run" option from the menu at the top of the .Rmd file and then choosing "Run Selected Line(s)".  Do this now with the code above. You will see your output in the console below. This allows you to see how your code is working without having to knit a html document.  

2. You can use variables to represent various kinds of objects (numbers, vectors, matrices, function output, and data frames, which we will explain later) in R.  

The assignment operator in R is `<-`. It assigns whatever is on the left hand side to have the value of whatever is on the right hand side.  In the following data chunk, we will assign the variable `x` to represent the number 5 and the variable `y` to represent the number 3.

Note: you can use the shortcut `option + -` on Mac or `alt + -` on Windows which will automatically surround the assignment operator with spaces. While `=` works as an assignment operator in R, it can sometimes cause problems so we suggest you stick with `<-`. RStudio offers many [handy keyboard shortcuts](https://support.rstudio.com/hc/en-us/articles/200711853-Keyboard-Shortcuts). Also, `option + shift + k` or `alt + shift + k` brings up a keyboard shortcut reference card.


We will now run the previous calculations using the variables x and y. 
```{r x_and_y_operations, eval=TRUE}
x <- 5
y <- 3
x - y
x + y
x * y
x / y
x ^ y
```
Change `eval=TRUE` so that this code will run in your html document file.

You don't need to use just one letter when assigning variables. You have quite a bit of leeway when it comes to naming variables. However variable names cannot start with a digit and cannot contain certain other characters such as a comma or a space.
You will be wise to adopt a convention for demarcating words in names.

```
i_use_snake_case
other.people.use.periods
evenOthersUseCamelCase
```
Finally we suggest you use names that are informative and that will help you understand your code when you reread it in the future.

In the code chunk below, come up with a descriptive variable name (using "snake case") for the maximum number of students in a section and assign the value 35 to it:
```{r}
Number_of_Students <- 35
```

We'll make another assignment:
```{r}
patrick_rocks <- 2 ^ 3
```

If we were to try to inspect the object (incorrectly) we would get the following errors:

```{r, eval=FALSE}
patrickrocks
#> Error in eval(expr, envir, enclos): object 'patrickrocks' not found
patrik_rocks
#> Error in eval(expr, envir, enclos): object 'patrik_rocks' not found
```

Implicit contract with the computer / scripting language: Computer will do tedious computation for you. In return, you will be completely precise in your instructions. Typos matter. Case matters.

Try setting `eval=TRUE` on the above code chunk. Two things happen when you try to knit your html document: 1) you will not get an updated html document and 2) an error message will pop up in the R Markdown tab of RStudio below. The important information from this error message is that the "object 'patrickrocks' is not found."  Now, set `eval=FALSE` so that you can again knit a html document from this .Rmd document.

Note, unless you clear your workspace, R "remembers" any previously defined variables.

3. All of your R Markdown documents and the R Console below have separate "workspaces."  Your workspace contains all of the variables you have defined in your R Markdown document or your console with their values.

Any variables that we defined in this R Markdown document that were not run through the R Console below are in the workspace for this .Rmd document, but not the workspace for the R Console.  The workspace of your R Console can be found under the "Environment" tab in the upper right window of RStudio.  Currently, this workspace should be empty since all code where we have assigned values to variables was run only by knitting a html document from the .Rmd document and not directly through the R Console.    

R code can be run directly through the R Console in three ways:

1) You can copy code from another document and paste it at the command prompt in your R Console.  

2) As mentioned above, you can highlight the code in your R Markdown document and choose "Run" from the menu for that document.  

3) You can type code in directly at the command prompt.  

Variables defined using any of these three methods will then be in the workspace for the R Console.


R has a mind-blowing collection of built-in functions that are accessed like so:


`functionName(argument1 = value1, argument2 = value2, and so on)`

Let’s try using seq() which makes regular sequences of numbers and, while we’re at it, demo more helpful features of RStudio.

Type `se` in the R console tab and hit TAB. A pop up shows you possible completions. Specify seq() by typing more to disambiguate or using the up/down arrows to select. Notice the floating tool-tip-type help that pops up, reminding you of a function’s arguments. If you want even more help, press F1 as directed to get the full documentation in the help tab of the lower right pane. Now open the parentheses and notice the automatic addition of the closing parenthesis and the placement of cursor in the middle. Type the arguments 1, 10 and hit return. RStudio also exits the parenthetical expression for you. Integrated Development Environments (IDEs) are great.

Assign `seq(1,10)` to a variable called `some_numbers` in the console. This variable is now in the workspace for the R console. Check to make sure you now see your variable defined under the "Environment" tab.


Notice `x` and `y` are not in the workspace for the R Console, they are only in the workspace of this R Markdown document.  Type `x` in the console below.  You should get the error message, "Error: object 'x' not found." 
You can put `x` and `y` in your console's workspace by either selecting the code in the chunk named `x_and_y_operations` and running it by pressing `cmd + enter` on Mac or `ctrl + enter` on Windows OR by highlighting this code and choosing "Run" from the menu above.  Please do this now.  Note that `x` and `y` are now in your workspace for the R console.


4. For any function in R for which you currently have the library for that function installed and loaded, all documentation for that function can be found by typing a question mark in front of the name of the function and running it in the R console.  For instance, to get documentation on the `getwd()` function, run the following R code by highlighting it and selecting "Run" from the menu above.


```{r}
?getwd
```

The documentation for `getwd` will now appear in the lower right window of Rstudio under the tab "Help."


5. Finally we need to check that you have a proper folder set up for the class.
We're going to use the function below to check that you have a BUAD 312 folder and in that folder there is a PS1 folder.
Don't worry about understanding what this function does, we're just going to call it.


```{r, echo=F}
# DO NOT CHANGE
check_folder_structure <- function(main_dir) {
  sub_dir = "PS1"
  folder_name_is_correct <-
    grepl(pattern = "BUAD312", x = main_dir)
  has_PS_folder <- dir.exists(file.path(main_dir, sub_dir))
  if (folder_name_is_correct) {
    print("You have correct folder name!")
  } else {
    print(
      "Hmm something is wrong with your folder name. Is your folder named BUAD312?"
    )
  }
  if (has_PS_folder) {
    print("You have a PS1 folder!")
  } else {
    print("Looks like you're missing a PS1 subfolder in your BUAD312 folder.")
  }
  
  return(folder_name_is_correct & has_PS_folder)
  
}
```


```{r, eval = F}
# An example of how to use the function using the path to my BUAD 312 folder 
check_folder_structure("/Users/patrick/Dropbox/Spring2020/BUAD312")
```


In the chunk below call the `check_folder_structure` function with the path to your BUAD 312 folder. 
I leave figuring out how to get the path to your BUAD 312 folder as an exercise. 
I suggest searching for *copy file path mac* or *copy file path windows*. 
Once you have found the path to your BUAD 312 folder call the `check_folder_structure` function with the path to your folder in the chunk below.


```{r}
check_folder_structure("/Users/wangxiaoming/Documents/BUAD312")
```

If successful, you will see output telling you that you have the correct folder name and an PS1 folder. If not, you will see output telling you where there might be an issue.


# What You Should Upload to Blackboard
Knit this .Rmd file into an html file and upload both files into Blackboad by the due date.






