---
title: "Problem Set 4"
output:
  html_document:
    highlight: pygments
    theme: cerulean
---
-----

### NAME: Jingyi Fang
### USC ID: 8020938911
### People I discussed this with:Jing Zhao, Jack Shi
### **DUE DATE: 2/20 at 11am **  

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#1.

We will use three R packages in this problem set.  (1) `tidyverse` (as always), (2) `moderndive` (from our textbook), and (2) the `nycflights13` R package (for the data set). **Write code in the code chunk below to load these two packages**

```{r question1}
#install.packages("moderndive")
#install.packages("nycflights13")
library(moderndive)
library(nycflights13)

```

#2. 
Create a new data frame called `df` with all flights occurring in January 2013 and with just two columns: the first column should give the number of seats in the plane and the second column should give the distance traveled by that plane in that flight.  Hint: You'll want to use the data frames `flights` and `planes`.


```{r question2}
library(nycflights13)
library(dplyr)
library(tidyverse)
library(lubridate)


df <- flights%>%
  filter(year == 2013, month == 1)%>%
  left_join(planes, by = "tailnum")%>%
  select(seats,distance)



```

#3.  
Make a plot that would help one to assess whether there is a relationship between the number of seats on a plane and the distance the plane travels. Include the line of best fit on this plot.  As always, be sure there is an informative title and informatively-labeled axes so that someone who doesn't know the data set will still understand what is being shown without asking questions.  Also, use `?flights` to look up the units of any variables so you can include these in the axis labels.

```{r question3}

ggplot(df,aes(x = seats, y = distance))+
  geom_point()+
  geom_smooth(method = "lm") +
  labs(x = "number of seats", y = "distance a plane travels(miles)", title = "The relationship between the number of seats on a plane and the distance the plane travels")

```

#4. 
Compute the correlation between the number of seats on a plane and the distance it travels.  Hint: Before computing the correlation, consider using `filter` to remove any flights with missing information.

```{r question4}
df%>%
  filter(!is.na(seats) & !is.na(distance))%>%
  summarize(correlation = cor(seats,distance))
```

#5.
Write code that fits the linear regression model and generates the regression table.

```{r question5}

fit <- lm(distance ~ seats, data = df)
get_regression_table(fit)

```

#6.
Imagine that you are sitting next to an off-duty pilot during a flight. Explain in words the meaning of the slope value that you calculated in the previous problem.

# The slope means that if the number of seats in a plane increses by 1 unit, the distance this plane travels will increase by 5.257 miles.

#7.
What would you expect the average distance of a flight to be for a plane with 160 seats? (Answer in words although if you produce a numeric estimate, please show your work by writing code.)

```{r question7}

fit <- lm(distance ~ seats, data = df)
get_regression_points(fit, newdata=tibble(seats = 160))
```

# The average distance will be 1150.845 miles.

#8.

```{r question8}

fit <- lm(distance ~ seats, data = df)
get_regression_points(fit, newdata=tibble(seats = 2000))

df%>%
  summarize(max_seats = max(seats,na.rm = TRUE))
```
Answer the same question as above, but with 2000 seats rather than 160.

# The maxmium seat in the df data set is 400. Thus, 2000 seats is an extrapolation. Thus, we can not predict a distance for a plane with 2000 seats. 


# What You Should Upload to Blackboard
Knit this .Rmd file into an html file. Upload both the .html and .Rmd files as a **single** .zip file to Blackboad by the due date. You can find instructions for making a .zip file on Piazza: https://piazza.com/class/k54ht3tm1d64u5?cid=11
